\section{Current Employment}

\cventry{2018 -- Current}{OCAD University PHASE Lab}{\textsc{Graduate Research Assistant}}{}{}{Develop algorithms to perform automatic and semi-automatic segmentation from various medical imaging technologies, using marching cube, histogram manipulation, seed based approaches, morphological filters and U-Net deep learning architecture.  Develop and implement a pipeline to generate image ready frame stacks for medical holography from segmented MRI data of rat, monkey, and human brain.  As well as worked with UHN to develop segmentation  of OCT vascular data for 3D medical holographic visualization.\\}

\cventry{2016 -- Current}{Headache Sciences Inc.}{\textsc{Chief Technology Officer}}{}{}{Develop the patent pending main algorithm of the company, to detect predisposition of migraine using machine learning and advanced signal processing techniques. Develop technical drawings and memos to communicate algorithm to a wide variety of academic and non-academic audience. Perform clinical data acquisition of patients for various pilot studies. Manage a team to identify medical regulation requirements, market research and venues of commercialization of the product. Create proposals for various grants and ethic boards which were successfully accepted.\\}

\cventry{2012 -- Current}{Cerebral Diagnostics Canada Inc.}{\textsc{Lead Developer and Biomedical Research Engineer}}{}{}{Develop various novel analytical tools to characterize and classify a variety of neurological processes. Created novel K-complex, alpha and delta analysis for sleep medicine using EEG source localization. Lead a group of mathematicians at the Fields Institute to develop a novel brain synchronization technique to identify brain region connectivity. Established a new protocol for VEP and LEP analysis for pain using EEG and source localization. Enhancing proficiency and performance of existing proprietary programs by optimizing code and merging programs. Programming proprietary robotic arm to test and measure thresholds of pain as it relates to diabetic neuropathy and carpal tunnel syndrome. Developing a new cap system for easy recording of EEG signals. Developed brain sonification techniques. Develop pipeline, analysis and program to transform existing brain imaging techniques into holographic print ready images.\\}