\section{Previous Employment}
% --------------------------------------------------------------------------------------------
\cventry{2018 -- 2020}{OCAD University PHASE Lab}{\textsc{Graduate Research Assistant} (Part-time)}{}{}{}
\cvlistitem{Develop algorithms to perform automatic and semi-automatic segmentation from various medical imaging technologies, using marching cube, histogram manipulation, seed based approaches, morphological filters and U-Net deep learning architecture.}
\cvlistitem{Develop and implement a pipeline to generate image ready frame stacks for medical holography from segmented MRI data of rat, monkey, and human brain.}
\cvlistitem{As well as worked with UHN to develop segmentation  of OCT vascular data for 3D medical holographic visualization.\\}

% --------------------------------------------------------------------------------------------
\cventry{2015 -- 2019}{Dementia Health}{\textsc{Data Scientist} (Part-time)}{}{}{}
\cvlistitem{Develop analytical tools to identify abnormalities in the EEG of Alzheimer\'s subjects to autonomously differentiate them from a normative group.}
\cvlistitem{ Develop novel signal processing techniques to perform feature analysis, reduction and fusion. Modify and identify appropriate existing machine learning techniques to perform pattern classification.}
\cvlistitem{Perform clinical data acquisition of patients for various pilot studies. Create proposals for various grants and ethic boards which were successfully accepted.\\}


% --------------------------------------------------------------------------------------------
\cventry{2015 -- 2018}{Cerebral Diagnostics Canada Inc.}{\textsc{Biomedical Research Engineer} (Full-time)}{}{}{}
\cvlistitem{Established a new protocol for visual and laser evoked potentials analysis for pain using EEG and source localization. Enhancing proficiency and performance of existing proprietary programs by optimizing code and merging programs.}
\cvlistitem{Programming proprietary robotic arm to test and measure thresholds of pain as it relates to diabetic neuropathy and carpal tunnel syndrome.}
\cvlistitem{Develop a new cap system for easy recording of EEG signals. Developed brain sonification techniques.}
\cvlistitem{Develop pipeline, analysis and program to transform existing brain imaging techniques into holographic print ready images.\\}

% --------------------------------------------------------------------------------------------
\cventry{2015 -- 2016}{University Health Network}{\textsc{Contract Programmer} (Part-time)}{}{}{}
\cvlistitem{Developed mobile apps for android and OS, as well as various web applications.}
\cvlistitem{These included creating a medical adherence app in which patient adherence were tracked and automatic reports were sent to doctors.\\}

% --------------------------------------------------------------------------------------------
\cventry{2011 -- 2015}{Cerebral Diagnostics Canada Inc.}{\textsc{Junior Biomedical Research Engineer and Programmer} (Part-time)}{}{}{}
\cvlistitem{Develop various novel analytical tools to characterize and classify a variety of neurological processes.}
\cvlistitem{Created novel K-complex, alpha and delta analysis for sleep medicine using EEG source localization.}
\cvlistitem{Lead a group of mathematicians at the Fields Institute to develop a novel brain synchronization technique to identify brain region connectivity. \\}

% --------------------------------------------------------------------------------------------
\cventry{2011 -- 2012}{Real Programming 4 Kids}{\textsc{Instructor} (Full-time)}{}{}{}
\cvlistitem{Taught children ages 7-15 about the fundamentals and good programming practices of computer programming using C++, C\#, Java and Visual Basics.}
\cvlistitem{Helped them develop computer games based on the knowledge gained in the course.}
\cvlistitem{Communicated effectively by using simple and clear terminology to explain complex terms.\\}

% --------------------------------------------------------------------------------------------
\cventry{2011 -- 2012}{Colours Without Borders}{\textsc{Research Assistant} (Part-time)}{}{}{}
\cvlistitem{Used C to acquire data from a device called the i1 pro to obtain colour information of a given colour bar.}
\cvlistitem{Analyzed raw spectrum of colour bar and successfully classified individual colours within a colour bar.}
\cvlistitem{Used C++ to create a graphical user interface(GUI) for pressman operators to maintain standard consistent colours within a printing job based on expected colour bar information and acquired colour bar information.}
\cvlistitem{The GUI communicated to a local and web server via SQL lite, to monitor the progression of a printing job.\\}


% --------------------------------------------------------------------------------------------
\cventry{2010 -- 2012}{Ryerson Signal Analysis Research Groups}{\textsc{Research Assistant} (Full-time)}{}{}{}
\cvlistitem{Used MATLAB to analyze spectrum and power densities of various EEG signals. Researched and developed algorithms to efficiently perform analysis.}
\cvlistitem{Used intelligent system classification techniques to group similar EEG signals. Developed a GUI in C\# and MATLAB to perform different algorithms on EEG signals.}
\cvlistitem{ Presented work and findings in weekly conference meetings.\\}

